\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{url}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  hidelinks
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Daksha Jha}
\address{Gwalior, Madhya Pradesh}
\address{%
  \href{mailto:dakshjha8085@gmail.com}{dakshjha8085@gmail.com} \\ 
  \href{https://linkedin.com/in/daksh-jha}{linkedin.com/in/daksh-jha} \\ 
  \href{https://github.com/0xdaksh-12}{github.com/0xdaksh-12}%
}

\begin{document}

% -----------------------------------------------------------------------
%  EDUCATION
% -----------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science}, ITM University Gwalior \hfill 2022 -- 2026 \\
CGPA: 7.0/10

{\bf Senior Secondary (Class XII)}, Rajendra Convent School, Bhind \\
Percentage: 64\%

{\bf Secondary (Class X)}, Rajendra Convent School, Bhind \\
Percentage: 71\%

\end{rSection}

% -----------------------------------------------------------------------
%  SKILLS
% -----------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Primary    & Java, TypeScript \\
Secondary  & SQL, Bash, Go, Python \\
Frontend   & React.js, TanStack Query/Router, Zustand \\
Backend    & NestJS, Gin, FastAPI \\
Databases  & PostgreSQL, MongoDB, Redis (Valkey) \\
Messaging  & RabbitMQ \\
Concepts   & Distributed Systems, OS, Computer Networks, gRPC \\
Tools      & Linux, Docker, Kubernetes, Git, GitHub Actions, Nginx \\
\end{tabular}

\end{rSection}

% -----------------------------------------------------------------------
%  PROJECTS
% -----------------------------------------------------------------------
\begin{rSection}{Projects}
\vspace{-1.25em}

\item \textbf{FluxTerm -- Shell Notebook} \hfill
  \href{https://github.com/0xflame-7/Flow}{GitHub} $|$
  \href{https://marketplace.visualstudio.com/items?itemName=0xflame-7.fluxterm}{VS Code Marketplace}\\
  Built a custom VS Code editor using a stateful webview architecture with a cross-platform execution engine supporting bash, zsh, PowerShell, and cmd. Implemented concurrent execution, DAG-based command chaining, and real-time stdout/stderr streaming. Added ANSI-aware rendering, smart output detection (JSON, CSV, media, URLs), and ensured state consistency under async workflows.

\item \textbf{fluxly -- Distributed URL Shortener} \hfill
  \href{https://github.com/0xflame-7/fluxly}{GitHub} $|$
  \href{https://fluxly.render.com/}{Live}\\
  Built a distributed URL shortener using microservices with NestJS, Go (Gin), and gRPC for inter-service communication. Designed an event-driven analytics pipeline using RabbitMQ and ClickHouse for high-throughput click tracking. Orchestrated services with Docker Compose and deployed on Kubernetes. Implemented Redis caching, PostgreSQL persistence, rate limiting, and custom short links with a React.js client and JWT/OAuth 2.0 authentication.

\item \textbf{Forge -- Workflow Engine} \hfill
  \href{https://github.com/0xflame-7/Forge}{GitHub}\\
  Built a self-hosted CI/CD-style system that triggers builds from Git events, executes jobs in isolated containers, and deploys to Kubernetes. Implemented pipeline workflows, logging, and status tracking with Docker-based execution and GitHub Actions integration, enabling automated testing and deployment in a local environment.

\end{rSection}

% -----------------------------------------------------------------------
%  ACHIEVEMENTS
% -----------------------------------------------------------------------
\begin{rSection}{Achievements}
\begin{itemize}
  \item \textbf{LeetCode:} Knight; solved 200+ problems across DSA
  \item \textbf{HackerRank:} 5$\star$ in C++, Problem Solving, SQL, Linux Shell
\end{itemize}
\end{rSection}

% -----------------------------------------------------------------------
%  CERTIFICATIONS
% -----------------------------------------------------------------------
\begin{rSection}{Certifications}
\begin{itemize}
  \item CS50x: Introduction to Computer Science --- Harvard University (edX)
  \item CS50 SQL: Introduction to Databases with SQL --- Harvard University (edX)
  \item AWS Academy Cloud Foundations --- Amazon Web Services
\end{itemize}
\end{rSection}

\end{document}
